Experimental Results \\ \mbox{ } \\ of a Safety Checker for Petri nets

### 2013-11-11 doc/experiments-2013-10-21.tex
Updated numbers in experiments

\begin{table}[h]
\begin{center}
  \begin{tabular}{ | r | p{6cm} | r | r | r | r | }
    \hline
    \multicolumn{2}{|l|}{Configuration} & pos & neg & don't know & TO \\
    \hline
    C1 & State constraint with real numbers & 16 &  0 & 11 &  0 \\
    C2 & State constraint with integers     & 16 &  0 & 11 &  0 \\
    \hline
    C3 & C2 + TrapConditions               & 20 &  0 &  7 &  0 \\
    C4 & C3 + SubnetTrapConditions         & 21 &  0 &  6 &  0 \\
    C5 & C4 + EmptyTrapConditions          & 21 &  0 &  6 &  0 \\
    \hline
    C9 & C4 + state space exploration \& TO 4\,h & 21 &  2 & 0 &  4 \\
    \hline
  \end{tabular}
\end{center}
\caption{Experimental results for the benchmarks of \mist}
\label{mist-experiments}
\end{table}

Observations:
\begin{itemize}
\item State constraints over integers or reals correctly determine that the 16 benchmarks in Appendix~\ref{mist-experiments-c1} are positive.
\item Composing state constraints with TrapConditions gives the following 4 additional positives.
\begin{verbatim}
PN/pingpong
boundedPN/lamport
boundedPN/newdekker
boundedPN/peterson
\end{verbatim}
\item Composing state constraints with TrapConditions and SubnetTrapConditions gives the additional positive \ttt{PN/manufacturing}.
  \item The remaining positive benchmarks are the following.
\begin{verbatim}
PN/extendedread-write
PN/extendedread-write-smallconsts
\end{verbatim}
\end{itemize}

>>>>

\begin{table}[h]
\begin{center}
  \begin{tabular}{ | r | p{6cm} | r | r | r | r | }
    \hline
    \multicolumn{2}{|l|}{Configuration} & pos & neg & don't know & TO \\
    \hline
    C1 & State constraint with real numbers & 14 &  0 & 13 &  0 \\
    C2 & State constraint with integers     & 14 &  0 & 13 &  0 \\
    \hline
    C3 & C2 + TrapConditions               & 20 &  0 &  7 &  0 \\
    C4 & C3 + SubnetTrapConditions         & 21 &  0 &  6 &  0 \\
    C5 & C4 + EmptyTrapConditions          & 21 &  0 &  6 &  0 \\
    \hline
    C9 & C4 + state space exploration \& TO 4\,h & 21 &  2 & 0 &  4 \\
    \hline
  \end{tabular}
\end{center}
\caption{Experimental results for the benchmarks of \mist}
\label{mist-experiments}
\end{table}

Observations:
\begin{itemize}
\item State constraints over integers or reals correctly determine that the 14 benchmarks in Appendix~\ref{mist-experiments-c1} are positive.
\item Composing state constraints with TrapConditions gives the following 6 additional positives.
\begin{verbatim}
PN/pingpong
PN/basicME
PN/multiME
boundedPN/lamport
boundedPN/newdekker
boundedPN/peterson
\end{verbatim}
\item Composing state constraints with TrapConditions and SubnetTrapConditions gives the additional positive \ttt{PN/manufacturing}.
  \item The remaining positive benchmarks are the following.
\begin{verbatim}
PN/extendedread-write
PN/extendedread-write-smallconsts
\end{verbatim}
\end{itemize}
